%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\documentclass[tikz,border=5mm]{standalone}

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Rui}{Costa}{Senior Software Developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside}{../data/photo} % In the aside, each new line forces a line break
\section{contact}
Rua Laureano Brito,\textnumero5 Casa 1
4910-519 Vila Praia de \^Ancora
Portugal
~
%\skype{rui.d.a.costa}
~
\email{ruiduartecosta@gmail.com}
\github{ruidacosta}
\linkedin{ruidcosta}
\section{languages}
Native portuguese
Fluent English \& Spanish
Basic french (A1)
\section{programming}
C++, C\#, Python,
PL/SQL,
Bash Scripting,
PHP, Java,
JavaScript,
CSS \& HTML5, Golang,
Rust
\section{frameworks}
NodeJS, AngularJS,
JQuery, Django,
Symfony
\section{tools}
Sqlite, MySql,
Oracle, PostgreSQL
MongoDB, Hadoop/Hive
Git, SVN,
Windows, Linux,
MacOS, Docker
\end{aside}

%----------------------------------------------------------------------------------------
%     PRESENTION
%----------------------------------------------------------------------------------------

\section{presentation}
% REDO TEXT
A versatile and professional graduate software developer with 10+ years of commercial experience. Worked with C++, C\#, Javascript and PL/SQL on Windows environments. Mac Os and Linux user with 10+ years of personal experience. \\
A proven ability to maintain and enhance company software with the aim of improving operational functionality in line with business requirement. \\
Able to work with any technology and to perform full software development life cycle activates.\\
Looking for a software developer opportunities that will allow me to work alongside an expert team of developers and on challenging projects in terms of technology and implementation. Thereby helping to drive my career progression, increasing experience in diferent technologies.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
    {2021--Now}
    {Natixis, Sucursal em Portugal - Sophis Stress Tests Commodities}
    {Senior Software Developer}
    {Porto, Portugal}
    {
        % WRITE TEXT
        Working directly with business analysts and business users, located in Paris and London, in order to implement his needs. Develop new features in existent backend applications, to improve the stress test calculations and user needs. Also fixing bugs and code optimization. Generating specific reports for users, and import calculation results to Hadoop database. Support on Sophis Commodities Stress Tests, with On Call support during the night and weekend.

        \textbf{Key Skills:}
        C++, C\#, Oracle Database, SQL Server, Hive, Hadoop, Windows Batch Scripting, Python, Git, Sophis API, Commodities
    }

%------------------------------------------------

%\entry
%    {2019--2021}
%    {Natixis, Sucursal em Portugal - Sophis Front-Office Equities}
%    {Senior Software Developer}
%    {Porto, Portugal}
%    {
%        Same as before.
%    }

%------------------------------------------------

\entry
    {2017--2021}
    {Natixis, Sucursal em Portugal - Sophis Front-Office Equities}
    {Software Developer}
    {Porto, Portugal}
    {
        % RE-Write text simplifying it
        Work directly with business analysts, located in Paris and London, in order to implement client needs. Develop new features in existent applications (Squall and Booster) used by clients to book and manage contracts of SLB (Stock Lending and Borrowing) and TRS (Total Return Swaps).  Create executables to generate specific client reports in csv files, and sending then by FTP or directly by email. Develop and manage communication on gateways with external SLB exchanges. Maintenance on existent applications, correcting bugs and optimising code. Second line support on Sophis Front Office - Equities.

        \textbf{Key Skills:}
        C\#, C++, Oracle Database, SQL Server, MySQL, WPF, Windows Batch Scripting, SVN, TFS, Git, Sophis, Equities
    }

%------------------------------------------------

\end{entrylist}

\pagebreak

\begin{entrylist}

\entry
    {2013--2017}
    {Finantech - Front-Office}
    {Software Developer}
    {Porto, Portugal}
    {
        % Re-write text simplifying it
        Build functions and procedures on Oracle Databases for all company's trading systems. Add features, using C\#, on a software designed to enable clients to configure their business rules. Fix bugs on trading server-side software, using C\# and C++. Maintain existing libraries for communication interfaces with market data providers updated, using C++. Develop a Web Interface for all server side trading systems, using AngularJS and JQuery on front-end and C++ on backend. Server side application to insert real-time market data on a DB2 database system. Support clients in European and American financial markets. 

        \textbf{Key Skills: }
        C++, C\#, Oracle Databases, HTML, Javascript, JQuery, AngularJS, DB2 Databases, Fix Protocol, HTTP, REST API, Multi-Threading
    }

%------------------------------------------------

\end{entrylist}

%\pagebreak

\subsection{Part Time}

\begin{entrylist}

\entry
{2006-2010}
{Freelancer}
    {Backend developer}
{}
{
Develop back-end for some small websites in PHP.  

\textbf{Key Skills: }
PHP, MySQL, Apache, HTML, Javascript
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entryedu
{2010--2013}
{Incomplete Master {\normalfont of Software Engineer}}
{University of Porto, Portugal}
{Specialization in Network and Distributed Systems.\\Thesis missing}

%------------------------------------------------

\entryedu
{2006--2010}
{Bachelor {\normalfont of Software Engineer}}
{University of Porto, Portugal}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} software development, software design, web app creation, real-time computing, high-throughput computing,  high-performance computing, parallel computing \textbf{personal:} shooting (sport), riding motorcycle, travelling, fishing, spearfishing

\end{document}
